Reaction & action alternatives

### 2023-05-19 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/reaction_action_alternatives.Rmd
action alternatives

### action alternatives count (sum score)
# t-test for expertise differences
t.test(x = main$count[main$id == "Expert"],
       y = main$count[main$id == "Novice"])

@@

# effect size for expertise differences
CohenD(x = main$nd[main$id == "Expert"],
       y = main$nd[main$id == "Novice"],
       na.rm = TRUE)
```

>>>>

### action alternatives count
# t-test for expertise differences
t.test(x = main$count[main$id == "Expert"],
       y = main$count[main$id == "Novice"])

@@
